Whitepaper: Contract Modules

### 2021-05-17 papers/contract-modules/modules.tex
tiny fix

\lstdefinelanguage{michelson}{
  % basicstyle=\ttfamily{},
  classoffset=0,
  morekeywords={parameter,storage,code},
  keywordstyle=\bfseries, 
  % predefined types
  classoffset=1,
  morekeywords={nat,int,unit,string,or,pair,option,address},
  keywordstyle=\color{blue},
  classoffset=2,
  morekeywords={CAR,CDR,CONS,DUP,EQ,FAILWITH,IF,IF_LEFT,LE,LEFT,NIL,DROP,PUSH,RIGHT,SENDER,SUB},
  keywordstyle=\color{magenta},
  backgroundcolor=\color{pink!20}
}

>>>>

\lstdefinelanguage{michelson}{
  % basicstyle=\ttfamily{},
  classoffset=0,
  morekeywords={parameter,storage,code},
  keywordstyle=\bfseries, 
  % predefined types
  classoffset=1,

  morekeywords={nat,int,unit,string,or,pair,option,address},
  keywordstyle=\color{blue},
  classoffset=2,
  morekeywords={CAR,CDR,CONS,DUP,EQ,FAILWITH,IF,IF_LEFT,LE,LEFT,NIL,DROP,PUSH,RIGHT,SENDER,SUB},
  keywordstyle=\color{magenta},
  backgroundcolor=\color{pink!20}
}
